\section{Part IV - Working with KIT's storage ring KARA}
KARA is a $2.5\,\mathrm{GeV}$ electron storage ring. It's fed from a $90\,\mathrm{keV}$ electron gun, followed by a $53\,\mathrm{MeV}$ mictrotron and a last booster synchrotron up to $500\,\mathrm{MeV}$ before injection into KARA.
\par
In order to fill some current into KARA at first 
The magnetic fields in the bending and focusing elements are cycled to remove the magnetic hysteresis; they need to be raised from the low amplitude required at beam injection, to a maximum value, corresponding to peak beam energy and back again so as to be ready to accept the next pulse of injected beam.
The magnets have to be set to the current suitable for the injection energy as well as the RF frequency and amplitude.
After the injections magnets are turned on.
Then the trigger needs to be started to give a timing reference so as to synchronise different parts and power supplies of the kicker and the other magnets and the injection can start. 
Once enough current is in the ring the trigger and injection magnets can be stopped.\\
After it stopped the vertical orbit correction is turned on and the the energy ramp can be started. 
Reaching a certain energy also the horizontal orbit correction can be turned on.\\
The insertion devices (wiggler/undulator) are opened.
\par
The energy ramp...
\par

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Part V - Network analyzer}
In this part a network analyzer is used to determine the properties of different devices.
\par
For two different coaxial cables, RG58 and RG59, the attenuation and reflection  for $50-1500\,\mathrm{MHz}$ are investigated.
The first one, RG58, has a characteristic impedance of $Z=\sqrt{\frac{L}{C}}=50\,\mathrm{\Omega}$
The reflection coefficient is $r=\left|\frac{\text{Reflected power}}{\text{Incident power}}\right|$ and thus the return loss is $10\cdot\log(r)$ in dB. Analogously for the transmission coefficient $t=\left|\frac{\text{Transmitted power}}{\text{Incident power}}\right|$.
%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Part VI - Cavity}